\documentclass[margin]{res} 
\textwidth=5.2in
\begin{document} 
\name{Abhi Agarwal - github.com/abhiagarwal\\[13pt]}
\begin{resume}
 
\section{Selected \\ Professional \\ Experience}

{\bf Software Engineer,} NYU Residential and Housing Department, New York, NY \hfill Jan-May 2014
 \begin{itemize} \itemsep -2pt
 \item Part of a team who built the next residential and housing platform at New York University using a C\# \& MSSQL stack on the back-end and Javascript on the front-end. Simplified housing process for students and administration at NYU.
 \end{itemize}

 {\bf Software Engineering Intern,} MedConsult, Bangkok, Thailand \hfill Jan-Aug 2011
 \begin{itemize} \itemsep -2pt
 \item Part of team in the development of an expert system for diagnosing diseases.
 \item Designed the client-side API, using Play in Java, to allow projects to utilize the medical database, and allow the use of external parameters for the expert system.
 \end{itemize}
 
\section{Selected \\ Projects}
 {\bf Lead Developer,} Nexious Medical \hfill Jan 2012-Aug 2013
 \begin{itemize} \itemsep -2pt
 \item Designed a machine learning algorithm, in Java, that implemented MedConsult's medical database to predict diseases individuals could have at different altitudes with different conditions.
 \item Developing a wearable device that would allow the user to enter his condition on a mobile app, and the wearable device would facilitate in diagnostics with information on the user's altitude, blood pressure, and temperature.
 \end{itemize}
 
 {\bf Side-project,} Dubsit.com \hfill August 2013-May 2014
 \begin{itemize} \itemsep -2pt 
 \item Developed a new way for individuals to search social content online (GIFs, Memes, etc), and developed a platform that ranks output from social media websites (Reddit, Quora, Pinterest, Tumblr, Twitter, bit.ly, etc.).
 \item Designed machine learning, and ranking algorithms, in Python, that rank content based on the statistics (upvotes, comments, shares, etc) from social media websites. Allowing users to get highest voted on content in social media quickly.
 \end{itemize}
 
{\bf Side-project,} Learnt.io \hfill May 2014-Present
\begin{itemize} \itemsep -2pt 
\item Platform too allow people to `store' things they learn as a part of their knowledge map, and relate that knowledge in the future. Built on NodeJS and MongoDB.
\item Building an artificial neural network to link information together, and to use this knowledge to give future suggestions on what things to learn.
\end{itemize}

\section{Education} 
- Bachelors of Art in Individualized Study at Gallatin, New York University. \\
- Thesis: "Engineering Creation" focusing on Computer Science, and Knowledge. \\
- Selected Classes: Artificial Intelligence, Compiler Construction, Machine Learning, Simulations, Basic Algorithms, and Computing with Large Datasets.

\section{Selected Achievements \\ and Activities} 
- Tech@NYU - E-Board, 2012-ongoing. Incharge of: HackDays. \\
- Duke of Edinburgh - For Gold Award -- climbed until Mt. Everest Base Camp in 2011, and for Silver Award -- reached summit of Mount Kinabalu in 2010. \\
- TEDxBangkokPatanaSchool - co-organized in 2011-2012, and TEDActive attendee in 2013. \\
- TechEX Thailand - Speaker, titled: ``My Journey through Computer Science", 2012.
- Most Improved Student Award at High School; Improved from C average to an A+ average.

\section{Technical \\ Skills}
- Excel in: Python; Javascript \& Node.JS; Java;  C++; Git; SQL/MYSQL; \\
- Experience with: PHP; Go; Visual Basics.NET; Ruby; C\#; C; Objective-C \& Swift (iOS); Android; Backbone.JS; Ruby on Rails; MongoDB; Redis; Apache; Nginx; Linux;

\end{resume} 
\end{document} 
