\documentclass[margin]{res} 
\textwidth=5.2in
\begin{document} 
\name{Abhi Agarwal - github.com/abhiagarwal\\[13pt]}
\begin{resume}
 
\section{Professional \\ Experience}

{\bf Software Engineer}, NYU Residential and Housing Department, New York, NY \hfill Jan-May 2014
\begin{itemize} \itemsep -2pt
\item Part of a team who build out the next residential and housing platform at New York University using a C\#/MSSQL stack on the back-end and Javascript on the front-end. Simplified housing process for students and administration at NYU.
\end{itemize}

{\bf Software Engineering Intern}, MedConsult, Bangkok, Thailand \hfill Jan-Aug 2011
\begin{itemize} \itemsep -2pt
\item Part of team in the development of an expert system for diagnosing diseases.
\item Designed the client-side API, using Play in Java, to allow projects to utilize the medical database, and allow the use of external parameters for the expert system.
\end{itemize}

{\bf Software Engineering Intern}, Aptech, Bangkok, Thailand \hfill June-Aug 2011
\begin{itemize} \itemsep -2pt
\item Worked with 3 companies to develop a comprehensive suite of server-side and client-side tools for jewelry management on a Visual Basics.NET/PHP/MYSQL stack. 
\item On average, for all 3 clients, this cut 13\% cost and increase revenue by 4\%.
\end{itemize}
 
\section{Selected \\ Projects}
 
{\bf Side-project}, Learnt.io \hfill May 2014-Present
\begin{itemize} \itemsep -2pt 
\item Platform too allow people to `store' things they learn as a part of their knowledge map, and relate that knowledge in the future. Built on NodeJS and MongoDB.
\item Building an artificial neural network to link information together, and to use this knowledge to give future suggestions on what things to learn.
\end{itemize}

{\bf Side-project}, Dubsit.com \hfill August 2013-May 2014
\begin{itemize} \itemsep -2pt 
\item Rethinking the way individuals search social content online, and creating a platform that ranks output from Social Media websites (Reddit, Quora, Pinterest, Tumblr, Twitter, bit.ly, etc.).
\item Designed Machine Learning, and ranking algorithms, in Python, that rank content based on the statistics (upvotes, comments, shares, etc) from social media websites. Allowing users to get highest voted on content in social media quickly.
\end{itemize}

 {\bf Lead Developer}, Nexious Medical \hfill Jan 2012-Aug 2013
 \begin{itemize} \itemsep -2pt
 \item Designed a machine learning algorithm, in Java, that implemented MedConsult's medical database to predict diseases individuals could have at different altitudes with different conditions.
 \item Developing a wearable device that would allow the user to enter his condition on a mobile app, and the wearable device would facilitate in diagnostics with information on the user's altitude, blood pressure, and temperature.
 \end{itemize}

{\bf Side-project}, Habless.com \hfill Jan 2005-Aug 2011
\begin{itemize} \itemsep -2pt 
\item Created a platform on a PHP/MYSQL stack, at age 12, which allowed over 32,000
unique visitors per month, to listen to live music, discuss games, and interact.
\item Licensed the back-end system to 62 clients at \$150 dollars a year, and also raised over \$10,000 of profit through sponsorships and advertisements.
\end{itemize}

\section{Research}

{\bf Research group}, \hfill Jan 2014-May 2014
\begin{itemize} \itemsep -2pt 
\item The Traveling Disease: stochastic evolution of a disease across an isolated system of four cities connected by roads.
\item Traffic: Steady-State Analysis of the One-Lane Roundabout.
\item N-body: Analysis of change in orbit when changing masses of planets in a solar system.
\end{itemize}

\section{Education} 
- Bachelors of Art in Individualized Study at Gallatin, New York University. \\
- Thesis: "Engineering Creation" focusing on Computer Science, and Knowledge. \\
- Classes: Compiler Construction, Computing with Large Datasets, Algorithmic Problem Solving, Artificial Intelligence, Physical Computing, Simulations, Computer Systems Organization, Basic Algorithms, Machine Learning, Dealing with Data, and Data Structures.

\section{Selected Achievements \\ and Activities} 
- Tech@NYU - E-Board, 2012-ongoing. Currently: HackDays \& Freshman Circuit. \\
- Duke of Edinburgh - Gold Award, climbed Mt. Everest Base Camp, 2011 and Silver Award, climbed Mount Kinabalu, 2010. \\
- TED - co-organized TEDxBangkokPatanaSchool in 2011-2012, and TEDActive attendee in 2013. \\
- TechEX Thailand - Speaker, titled: ``My Journey through Computer Science", 2012.
- Most Improved Student Award at High School; Improved from C average to an A+ average.

\section{Technical \\ Skills}
- Excel in: Python; Javascript \& Node.JS; Java;  C++; Git; SQL/MYSQL; \\
- Experience with: PHP; Go; Visual Basics.NET; Ruby; C\#; C; Objective-C \& Swift (iOS); Android; Backbone.JS; Ruby on Rails; MongoDB; Redis; Apache; Nginx; Linux;

\end{resume} 
\end{document} 
